---
title: "Group5Project"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Group5Project}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
#library(devtools)
devtools::load_all()
library(Group5Project)
```

This vignette summarises the main functions in our package.

## pooledPValues
This is the main function of the package: it is the only exported function, and as such the only function that the user should interface with. It pools the p-values between data frames using the specified method. 

Usage: pooledPValues(method = "Fisher", ...)

The possible pooling method arguments are:

* "Fisher" for Fisher

* "Stouffer" for Stouffer

* "minP" for Minimum P-value

* "maxP" for Maximum P-value

The data frames to pool the p-values from are to be passed as arguments after the method specification argument. There must be between 2 and 5 data frames, all with the same number of columns, and at least 2 groups per data frame.

The output is a vector of the pooled p-values for each biomarker. For p biomarkers, the vector will be of length p.

```{r}
set.seed(123)
p<-100
data1 <- data.frame(group=sample(1:3,200,replace=TRUE),matrix(rnorm(p*200),ncol=p))
data2 <- data.frame(group=sample(1:2,150,replace=TRUE),matrix(rnorm(p*150),ncol=p))
pooledPValues(method = "Fisher",data1,data2)
```
```{r}
pooledPValues(method = "Stouffer",data1,data2)
```
```{r}
pooledPValues(method = "minP",data1,data2)
```
```{r}
pooledPValues(method = "maxP",data1,data2)
```

## getFramePvals
This non-exported function tests for normality within groups as well as homoskedasticity between groups, then applies the appropriate test for group difference. The return value is a vector of the resulting p-values. 

```{r}
set.seed(123)
p<-100
data1 <- data.frame(group=sample(1:3,200,replace=TRUE),matrix(rnorm(p*200),ncol=p))
getFramePvals(data1)
```

## isInputValid
This non-exported function tests to see if the input to the main function is valid. Valid input is defined as 2-5 data frames, each with:

* The same number of columns.

* At least 2 unique values in the first column.

```{r}
set.seed(123)
p<-100
data1 <- data.frame(group=sample(1:3,200,replace=TRUE),matrix(rnorm(p*200),ncol=p))
data2 <- data.frame(group=sample(1:2,150,replace=TRUE),matrix(rnorm(p*150),ncol=p))
isInputValid(list(data1,data2))
```
```{r}
set.seed(123)
p<-100
data1 <- data.frame(group=sample(1:3,200,replace=TRUE),matrix(rnorm(p*200),ncol=p))
a<-list(data1,data1,data1,data1,data1,data1)
isInputValid(a)
```

## isNormByGroup
This non-exported function determines if a biomarker is normally distributed by group at alpha level 0.05. Note that the shapiro.test() function limits sample size to 5000.

Usage: isNormByGroup(dataFrame, marker)

Marker is the biomarker number to be tested; e.g., for the nth biomarker, input integer n. Note that marker n corresponds to column n+1 in the data frame.
```{r}
isNormByGroup(data1,3)
```
```{r}
set.seed(123)
p<-100
data3 <- data.frame(group=sample(1:3,200,replace=TRUE),matrix(rexp(p*200),ncol=p))
isNormByGroup(data3,4)
```
